---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  eval = F
)
```

# Rdirectlfq

<!-- badges: start -->
<!-- badges: end -->

`Rdirectlfq` is an R package that runs the `directlfq` Python library to calculate protein abundance using ion abundance.

## Installation

You can install the development version of Rdirectlfq like so:

``` r
devtools::install_github("mildpiggy/directlfq")
```

## Requirement

The packages require a python conda environment with dircetlfq library. Your can check and deploy this conda environment by `check_directlfq_Module`

```{r}
check_directlfq_Module(confirm_or_not = T)
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(Rdirectlfq)
data(example_diann_res) ## A diann result from report.tsv
pro_int = directlfq(example_diann_res,reformatted = F)

## A generic input table, which has been reformatted.
data(example_generic_input)
pro_int = directlfq(example_generic_input, reformatted = T)
```

For more detailed information on the input table, please refer to the GitHub repository of MannLabs: https://github.com/MannLabs/directlfq.

## Q&A

Any issues encountered during the use can be submitted through the issue tracker or by contacting the developer.


